---
title: "Code Along 7"
author: "Chee Ting"
date: "2023-10-04"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r, eval=TRUE,echo=TRUE}
library(tidyverse)
install.packages("palmerpenguins")
library(palmerpenguins)
glimpse(penguins)

```

```{r,eval=TRUE,echo=TRUE}

ggplot(data = penguins)

```
```{r,eval=TRUE,echo=TRUE}
#  Map bill depth to the x-axis
ggplot(data = penguins,
mapping = aes(x = bill_depth_mm))

```
```{r,eval=TRUE,echo=TRUE}
#Map bill length to the y-axis

ggplot(data = penguins,
mapping = aes(x = bill_depth_mm,
y = bill_length_mm))
```
```{r,eval=TRUE,echo=TRUE}
# Represent each observation with a point
ggplot(data = penguins,
mapping = aes(x = bill_depth_mm,
y = bill_length_mm)) +
geom_point()
```
```{r,eval=TRUE,echo=TRUE}
# Map species to the colour of each point
ggplot(data = penguins,
mapping = aes(x = bill_depth_mm,
y = bill_length_mm,
colour = species)) +
geom_point()
```
```{r,eval=TRUE,echo=TRUE}
# Title the plot "Bill depth and length
ggplot(data = penguins,
mapping = aes(x = bill_depth_mm,
y = bill_length_mm,
colour = species)) +
geom_point() +
labs(title = "Bill depth and length")
```
```{r,eval=TRUE,echo=TRUE}
# Add the subtitle "Dimensions for Adelie, Chinstrap, and Gentoo Penguins"

ggplot(data = penguins,
mapping = aes(x = bill_depth_mm,
y = bill_length_mm,
colour = species)) +
geom_point() +
labs(title = "Bill depth and length",
subtitle = "Dimensions for Adelie,
Chinstrap, and Gentoo Penguins")
```
```{r,eval=TRUE,echo=TRUE}
#  Label the x and y axes as "Bill depth (mm)" and "Bill length (mm)", respectively

ggplot(data = penguins,
mapping = aes(x = bill_depth_mm,
y = bill_length_mm,
colour = species)) +
geom_point() +
labs(title = "Bill depth and length",
subtitle = "Dimensions for Adelie, Chinstrap",
x = "Bill depth (mm)",
y = "Bill length (mm)")


```


```{r,eval=TRUE,echo=TRUE}
### Label the legend "Species"
ggplot(data = penguins,
mapping = aes(x = bill_depth_mm,
y = bill_length_mm,
colour = species)) +
geom_point() +
labs(title = "Bill depth and length",
subtitle = "Dimensions for Adelie, Chinstrap",
x = "Bill depth (mm)", y = "Bill length (mm)", 
colour = "Species")
```

```{r,eval=TRUE,echo=TRUE}
### Add a caption for the data sourceggplot(data = penguins
mapping = aes(x = bill_depth_mm,
y = bill_length_mm,
colour = species)) +
geom_point() +
labs(title = "Bill depth and length",
subtitle = "Dimensions for Adelie, Chinstrap",
x = "Bill depth (mm)", y = "Bill length (mm)", 
colour = "Species",
caption = "Source: Palmer Station LTER")
```


```{r,eval=TRUE,echo=TRUE}
###  Finally, use a discrete colour scale that is designed to be perceived by viewers with common forms of colour blindness.
ggplot(data = penguins,
mapping = aes(x = bill_depth_mm,
y = bill_length_mm,
colour = species)) +
geom_point() +
labs(title = "Bill depth and length",
subtitle = "Dimensions for Adelie, Chinstrap",
x = "Bill depth (mm)", y = "Bill length (mm)", 
colour = "Species",
caption = "Source: Palmer Station LTER")

scale_colour_viridis_d()


```
### Omit the names of first two arguments when building plots with ggplot()
```{r,eval=TRUE,echo=TRUE}
ggplot(penguins) + # Data layer
aes(x = bill_depth_mm,
y = bill_length_mm,
colour = species) + # Aesthetics layer
geom_point() + # Geometric layer
scale_colour_viridis_d()
```
### Feature 1: Colour
```{r,eval=TRUE,echo=TRUE}
ggplot(penguins) + aes(x = bill_depth_mm, y = bill_length_mm,
colour = species) +
geom_point() + scale_colour_viridis_d()
```
### Feature 2: Shapes
```{r,eval=TRUE,echo=TRUE}
ggplot(penguins) + aes(x = bill_depth_mm, y = bill_length_mm,
colour = species, shape = species) +
geom_point() + scale_colour_viridis_d()
```
### Feature 3: Sizes
```{r,eval=TRUE,echo=TRUE}
ggplot(penguins, aes(x = bill_depth_mm, y = bill_length_mm, colour = species, shape = species,
size = body_mass_g)) +
geom_point() + scale_colour_viridis_d()
```
### Feature 4: Alpha (Transparency)
```{r,eval=TRUE,echo=TRUE}
ggplot(penguins, aes(x = bill_depth_mm, y = bill_length_mm, colour = species,
shape = species, size = body_mass_g, alpha = flipper_length_mm)) +
geom_point() + scale_colour_viridis_d()
```
### Mapping VS Setting
```{r,eval=TRUE,echo=TRUE}
ggplot(penguins) +
aes(x = bill_depth_mm,
y = bill_length_mm,
size = body_mass_g,
alpha = flipper_length_mm) +
geom_point()
```
### Mapping VS Setting
```{r,eval=TRUE,echo=TRUE}
ggplot(penguins) +
aes(x = bill_depth_mm,
y = bill_length_mm) +
geom_point(size = 2, alpha = 0.5)
```
### Faceting
```{r,eval=TRUE,echo=TRUE}
ggplot(penguins) +
aes(x = bill_depth_mm,
y = bill_length_mm) +
geom_point() +
facet_grid(species ~ island)
```
### Facet 2
```{r,eval=TRUE,echo=TRUE}
ggplot(penguins, aes(x = bill_depth_mm, y = bill_length_mm)) + geom_point() +
facet_grid(species ~ sex)
```
### Facet 3 
```{r,eval=TRUE,echo=TRUE}
ggplot(penguins, aes(x = bill_depth_mm, y = bill_length_mm)) + geom_point() +
facet_grid(sex ~ species)
```

### Facet 4
```{r,eval=TRUE,echo=TRUE}
ggplot(penguins, aes(x = bill_depth_mm, y = bill_length_mm)) + geom_point() +
facet_wrap(~ species)
```
### Facet 5
```{r,eval=TRUE,echo=TRUE}
ggplot(penguins, aes(x = bill_depth_mm, y = bill_length_mm)) + geom_point() +
facet_wrap(~ species, ncol = 2)
```
### Facet 6
```{r,eval=TRUE,echo=TRUE}
ggplot(penguins, aes(x = bill_depth_mm, y = bill_length_mm)) + geom_point() +
facet_grid(. ~ species)
```

### Facet and colour
```{r,eval=TRUE,echo=TRUE}
ggplot(penguins, aes(x = bill_depth_mm, y = bill_length_mm, color = species)) +
geom_point() + facet_grid(species ~ sex) + scale_color_viridis_d()
```
### Facet and colour, no legend
```{r,eval=TRUE,echo=TRUE}
ggplot(penguins, aes(x = bill_depth_mm, y = bill_length_mm, color = species)) +
geom_point() + facet_grid(species ~ sex) + scale_color_viridis_d() +
guides(color = "none")
```
```{r,eval=TRUE,echo=TRUE}
library(openintro)
glimpse(loans_full_schema)
```
```{r,eval=TRUE,echo=TRUE}
loans <- loans_full_schema %>%
select(loan_amount, interest_rate, term, grade,
state, annual_income, homeownership, debt_to_income)
glimpse(loans)
```
### Histograms
```{r,eval=TRUE,echo=TRUE}
ggplot(loans) + aes(x = loan_amount) +
geom_histogram()
```

```{r,eval=TRUE,echo=TRUE}
# binwidth = 1000
ggplot(loans, aes(x = loan_amount)) +
geom_histogram(binwidth = 1000)
```
```{r,eval=TRUE,echo=TRUE}
# binwidth = 5000
ggplot(loans, aes(x = loan_amount)) +
geom_histogram(binwidth = 5000)
```
```{r,eval=TRUE,echo=TRUE}
# binwidth = 2000
ggplot(loans, aes(x = loan_amount)) +
geom_histogram(binwidth = 2000)
```
```{r,eval=TRUE,echo=TRUE}
# Customising Histograms
ggplot(loans, aes(x = loan_amount)) + geom_histogram(binwidth = 5000) +
labs(x = "Loan amount ($)", y = "Frequency", title = "Amounts of Lending Club loans" )
```
### Fill with a categorical variable
```{r,eval=TRUE,echo=TRUE}
ggplot(loans, aes(x = loan_amount, fill = homeownership)) +
geom_histogram(binwidth = 5000, alpha = 0.5) +
labs(x = "Loan amount ($)",y = "Frequency",title = "Amounts of Lending Club loans")
```

### Facet with a categorical variable
```{r,eval=TRUE,echo=TRUE}
ggplot(loans, aes(x = loan_amount, fill = homeownership)) + geom_histogram(binwidth = 5000) +
labs(x = "Loan amount ($)",y = "Frequency",title = "Amounts of Lending Club loans") +
facet_wrap(~ homeownership, nrow = 3)
```

### Density plot
```{r,eval=TRUE,echo=TRUE}
ggplot(loans, aes(x = loan_amount)) +
geom_density()
```

### Density plots and adjusting bandwidth
```{r,eval=TRUE,echo=TRUE}
ggplot(loans, aes(x = loan_amount)) +
geom_density(adjust = 0.5)
```


```{r,eval=TRUE,echo=TRUE}
ggplot(loans, aes(x = loan_amount)) +
geom_density(adjust = 1) # default bandwidth
```
```{r,eval=TRUE,echo=TRUE}
ggplot(loans, aes(x = loan_amount)) +
geom_density(adjust = 2)
```

### Customising density plots
```{r,eval=TRUE,echo=TRUE}
ggplot(loans, aes(x = loan_amount)) +
geom_density(adjust = 2) +
labs( x = "Loan amount ($)", y = "Density", title = "Amounts of Lending Club loans" )
```
### Adding a categorical variable
```{r,eval=TRUE,echo=TRUE}
ggplot(loans, aes(x = loan_amount, fill = homeownership)) +
geom_density(adjust = 2, alpha = 0.5) +
labs(x = "Loan amount ($)",y = "Density",title = "Amounts of Lending Club loans", fill = "Homeownership")
```
### Boxplot
```{r,eval=TRUE,echo=TRUE}
ggplot(loans, aes(x = interest_rate)) +
geom_boxplot()
```
### Box plot and outliers
```{r,eval=TRUE,echo=TRUE}
ggplot(loans, aes(x = annual_income)) +
geom_boxplot()
```

### Customizing box plots
```{r,eval=TRUE,echo=TRUE}
ggplot(loans, aes(x = interest_rate)) +geom_boxplot() +labs(x = "Interest rate (%)",y = NULL,
title = "Interest rates of Lending Club loans") +
theme( axis.ticks.y = element_blank(), axis.text.y = element_blank() )
```
### Adding categorical variable
```{r,eval=TRUE,echo=TRUE}
ggplot(loans, aes(x = interest_rate,
y = grade)) +
geom_boxplot() +
labs(x = "Interest rate (%)",y = "Grade",title = "Interest rates of Lending Club loans",subtitle=" By grade of loan")
```
### Scatterplot
```{r,eval=TRUE,echo=TRUE}
ggplot(loans, aes(x = debt_to_income, y = interest_rate)) +
geom_point()
```
### Hexplot
```{r,eval=TRUE,echo=TRUE}
ggplot(loans, aes(x = debt_to_income, y = interest_rate)) +
geom_hex()


```
```{r,eval=TRUE,echo=TRUE}
ggplot(loans %>% filter(debt_to_income < 100),
aes(x = debt_to_income, y = interest_rate)) +
geom_hex()
```
### Bar plot
```{r,eval=TRUE,echo=TRUE}
ggplot(loans, aes(x = homeownership)) +
geom_bar()
```
### Segmented Barplot
```{r,eval=TRUE,echo=TRUE}
ggplot(loans, aes(x = homeownership,
fill = grade)) +
geom_bar()
```
```{r,eval=TRUE,echo=TRUE}
ggplot(loans, aes(x = homeownership, fill = grade)) +
geom_bar(position = "fill")
```
### Customising bar plots
```{r,eval=TRUE,echo=TRUE}
ggplot(loans, aes(y = homeownership, fill = grade)) + geom_bar(position = "fill") +
labs( x = "Proportion", y = "Homeownership", fill = "Grade", title = "Grades of Lending Club loans")
```
### violin plot
```{r,eval=TRUE,echo=TRUE}
ggplot(loans, aes(x = homeownership, y = loan_amount)) +
geom_violin()
```
### Ridge Plots
```{r,eval=TRUE,echo=TRUE}
install.packages("ggridges")
library(ggridges)
ggplot(loans, aes(x = loan_amount, y = grade, fill = grade, color = grade)) +
geom_density_ridges(alpha = 0.5)
```

