---
title: "Final Project Submission - Week 10"
author: "Chee Ting"
date: "2023-10-16"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
**Week 9**

1) The topic that I have chosen for this project will be "Inflation". For this project, I will be investigating inflation rates worldwide and most importantly Singapore, analysing its global trends and the factors contributing to its rise or fall.

2) The data sources that I have curated so far are Inflation data by International Monetary Fund and Core Inflation of Singapore by Monetary Authority of Singapore.


**Week 10**

1) Why is inflation happening in Singapore?


2) 
- According to Monetary Authority Singapore,inflation affects many areas of the economy hence there is a need to understand inflation to secure a low and stable inflation in the Singapore economy over time.
- Singapore has the second highest inflation rate in 2023 among the ASEAN 5 countries according to the data provided by International Monetary Fund.
- Inflation in Singapore has been persistently growing according to data from Monetary Authority Singapore.



3) For the dataset "Inflation_world", I will be using the columns of 'region' and 'Inflation_rate'.

```{r, eval=TRUE,echo=FALSE}
library(tidyverse)
read_csv("Inflation_world.csv")
```
For the dataset "ASEAN_5_IMF", I will be using the columns of 'Year', 'Inflation_rate' and 'Country'.
```{r, eval=TRUE,echo=FALSE}

read_csv("Asean_5_IMF.csv")
```
For the dataset "Inflation_SG", I will be using the columns of 'Year' and 'Inflation_rate'.
```{r, eval=TRUE,echo=FALSE}

read_csv("Inflation_SG_IMF.csv")

```
For the dataset "CPI_goods", I will be using the columns of 'Goods' and 'Weights'.
```{r, eval=T,echo=FALSE}
read_csv("CPI_goods_singstat.csv")

```